Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Minor revision.

The way we generate a goal configuration is the following:
\begin{enumerate}
\item \textbf{Shoot a random configuration $q_{rand}$ in $\mathcal{C}$ with
  uniform distribution.}
\item \textbf{Call SolveConstraints (Algorithm~\ref{algo:newton}) on
  $q_{rand}$, with $f(q)$ defined by the intersection of the planning
  and goal manifolds $\manifold \cap \goalmanifold$.}
\item If success, check for collisions.
\end{enumerate}

@@

\begin{algorithm}[h]
  \caption{ConstrainedExtend($\mathcal{T},q_{near},q_{rand},f,\epsilon$)}
  \label{alg:constrained}
  \begin{algorithmic}
    \STATE {\color{red} // $I$ denotes the identity matrix.}
    \STATE $q_{rand}' \leftarrow q_{near} +   
    \left(I -  
    \left(\frac{\partial f}{\partial q}(q_{near})\right)^{+}
    \frac{\partial f}{\partial q}(q_{near})\right) (q_{rand} - q_{near})$
    \IF {$\texttt{SolveConstraints}(q_{rand}',f,\epsilon) = q_{rand}''$}
    \STATE RRT::Extend($\mathcal{T},q_{near},q_{rand}''$)
    \ENDIF
  \end{algorithmic}
\end{algorithm}

>>>>

The way we generate a goal configuration is the following:
\begin{enumerate}
\item \textbf{Shoot a random configuration $q_{rand}$ in $\mathcal{C}$ with
  uniform distribution.}
\item \textbf{Call \texttt{SolveConstraints} (Algorithm~\ref{algo:newton}) on
  $q_{rand}$, with $f(q)$ defined by the intersection of the planning
  and goal manifolds $\manifold \cap \goalmanifold$.}
\item If success, check for collisions.
\end{enumerate}

@@

\begin{algorithm}[h]
  \caption{\texttt{ConstrainedExtend}($\mathcal{T},q_{near},q_{rand},f,\epsilon$)}
  \label{alg:constrained}
  \begin{algorithmic}
    \STATE {\color{red} // $I$ denotes the identity matrix.}
    \STATE $q_{rand}' \leftarrow q_{near} +   
    \left(I -  
    \left(\frac{\partial f}{\partial q}(q_{near})\right)^{+}
    \frac{\partial f}{\partial q}(q_{near})\right) (q_{rand} - q_{near})$
    \IF {$\texttt{SolveConstraints}(q_{rand}',f,\epsilon) = q_{rand}''$}
    \STATE RRT::Extend($\mathcal{T},q_{near},q_{rand}''$)
    \ENDIF
  \end{algorithmic}
\end{algorithm}
